\section{Discussion and Limitations}

WhiteTiger provides a standardized and temporally structured data foundation for embodied intelligence research at billion-frame scale. Its principal properties are fully human-teleoperated physical collection, 13-platform embodiment coverage, preservation of platform-specific observation and action schemas, LeRobot v2.1 conversion, and event-level temporal annotations. With \textbf{9521.75 hours}, \textbf{513575 episodes}, and more than \textbf{1.03 billion frames}, the corpus supports foundation-model adaptation regimes that are difficult to evaluate with smaller task-specific datasets.

The offline zero-shot benchmark provides evidence for action-prediction transfer under a defined evaluation protocol. The evaluation datasets are external to WhiteTiger and excluded from WhiteTiger training. Across 13 platforms and 42 paired task-dataset records, the GR00T N1.6 model fine-tuned on WhiteTiger reduces Normalized ALL MSE and Normalized Joint MSE relative to the no-training baseline. Each task-level result averages five evaluation trajectories, and both models are evaluated on identical trajectories. The result supports dataset-level transfer to separately collected robot demonstration data.

WhiteTiger event annotations provide temporal structure beyond dense action labels. They expose task progress, subgoal completion, contact transitions, alignment states, boundary crossings, deformation states, and object-state changes that are often implicit in raw trajectories. This structure supports keyframe-aware learning paradigms, including waypoint-conditioned imitation learning, goal-conditioned policy learning, hierarchical skill decomposition, reward shaping, value-guided policy improvement, subgoal-image reasoning, and phase-aware evaluation. The annotations should be interpreted as a general temporal supervision resource rather than labels optimized for a single algorithm.

The current benchmark is an offline action-prediction evaluation, not a complete measure of real-world robot performance. Open-loop normalized MSE measures agreement with reference teleoperation actions under recorded observations, but it does not evaluate closed-loop recovery, contact-rich interaction stability, or task success under policy-induced state distributions. Sequential decision making can compound prediction errors as future observations shift away from demonstration trajectories~\cite{ross2011dagger,zhao2023aloha}. The benchmark demonstrates dataset-level transfer because the evaluation datasets are external to WhiteTiger, but it should not be interpreted as held-out-platform generalization when the evaluated robot platform is represented in WhiteTiger.

The completed benchmark uses one model family and one training regime: GR00T N1.6 under offline open-loop evaluation after one epoch of full fine-tuning. Additional baselines such as ACT, Behavior Transformer, Diffusion Policy, and open-source vision-language-action policies would broaden comparative coverage~\cite{zhao2023aloha,shafiullah2022behaviortransformer,chi2023diffusionpolicy,kim2024openvla}. Data-scaling studies, held-out-platform evaluation, closed-loop robot rollouts, trajectory-weighted aggregation, and uncertainty estimates across evaluation trajectories are required to characterize which dataset factors govern policy scaling and generalization.

Event- and keyframe-level annotations remain a dataset capability and a reserved experimental direction in the current version. The planned real-world evaluation of event-guided value learning has not yet been completed. Claims about improved real-robot execution from event-derived supervision should therefore be deferred until policies trained with and without event-based value signals are compared under identical closed-loop tasks with execution success rate, event completion rate, failure stage distribution, and time-to-completion metrics.
